### 2015-03-01 fundamentals/impl.tex
fix discussion of decay modes
Flanagan edits

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: cluster-ready software and dynamic libraries.  The
\gls{ABM} framework is then described, focusing on how \gls{ABM} is implemented
in a fuel cycle context and the relative benefits thereof. A discussion of the
time-dependent treatement of discrete resources follow, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials store the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 2 decay modes, with 2 additional
modes likely to be added in future releases:

>>>>

A modular, \acrfull{ABM} approach is ideal for solving complex, coupled,
physics-dependent supply chain problems involving material routing, facility
deployment, and regional and institutional hierarchies. Additionally, the choice
to build \Cyclus on open source libraries in modern programming languages
enables both remote and multiprocess execution on a number of platforms. This
section begins by describing the general design features that make \Cyclus both
flexible and powerful: cluster-ready software and dynamic libraries.  The
\gls{ABM} framework is then described, focusing on how \gls{ABM} is implemented
in a fuel cycle context and the relative benefits thereof. A discussion of the
time-dependent treatement of discrete resources follows, focusing on the
\gls{DRE}. Support for users and developers via the \Cycamore library of
archetypes and the experimental toolkit are also presented.  Lastly, the methods
for quality assurance are outlined.

@@

The \Cyclus kernel has built-in experimental support for decay calculations.
Materials store the time since their last decay and agents are free to
invoke the decay function on them as desired to decay them to the current
simulation time. \Cyclus can currently operate in 3 decay modes, with 1 additional
mode likely to be added in a future release:
